% !TEX TS-program = pdflatexmk
\documentclass[12pt]{nsf-proposal}

\newcommand{\dol}[2][]{\SI{#2}[\$]{#1}}
% use as \dol[\mega\relax]{1} for $1M, \dol{123} for $123.
\usepackage[sorting=none,sortcites=true,citestyle=numeric-comp]{biblatex}
\setlength\bibitemsep{\baselineskip}
\addbibresource{nsf-demo.bib}
\begin{document}
\chapter*{Project Summary} % 1 page max

\section*{Overview}

TN Tech has nearly doubled its amount of externally-funded research from \dol[\mega\relax]{11} in 2015 to \dol[\mega\relax]{20} in 2020, and plans to reach \dol[\mega\relax]{40} of externally-funded research by 2025.

\section*{Intellectual Merit}

The acquisition of Warp~1 will enable research projects aligned with four of NSF's 10 Big Ideas.

\section*{Broader Impacts}

TN Tech has a strong history using HPC in workforce development at all levels.

\chapter{Project Description}

\section{Information about the Proposal}

\begin{description}[labelwidth=1.7in,leftmargin=\labelwidth,labelsep=0pt]
\item[Instrument Location:] Tennessee Tech University, Clement Hall Room NNN
\item[Instrument Type:] HPC cluster with high-speed networking and data storage for active jobs
\end{description}

\section{Research Activities to be Enabled}

This cluster will provide an easily-accessible computing facility that immediately benefits TN Tech's research efforts across several departments and research centers to advance both fundamental and applied research in science and engineering.

\subsection{Intellectual Merit}

The proposed Warp~1 cluster will enable research projects aligned with four of NSF's 10 Big Ideas.

\subsection{Users and Representative Scientific Research}

\begin{table}
\centering
\caption{\label{tab:users} Selection of externally-supported users impacted by the proposed equipment}
\begin{tabular}{P{1.7in}P{1.5in}P{1.6in}P{1.25in}} \toprule
{\bfseries Field} & {\bfseries User} & {\bfseries Applications} & {\bfseries Support} \\ \midrule
Department 1 & Faculty 1 & Materials science & NSF \\
             & Faculty 2 & Molecular dynamics & CWRU, DOD \\ \addlinespace

Department 2 & Faculty 3 & Fundamental science & NSF \\ \bottomrule
\end{tabular}
\end{table}

This section details a selection of research projects.

\subsubsection{Next-Generation Genomics: Faculty 1, Department 1; Faculty 2, Department 2; Faculty 3, Department 3 (Other University)}

(5 faculty, 1 postdoc, 7 graduate students, 2 undergraduate students)
Funded projects in our labs use HPC resources to (1) generate genome-wide DNA data to inform on the management of endangered species \cite{torkamaneh2016}, (2) survey community composition based on DNA extracted from environmental sources \cite{watts2019}, and (3) investigate evolutionary processes in model organisms \cite{hurt2021}.

\section*{Broader Impacts}

Here we have a statement of broader impacts, which is often required as its own heading.

\subsection{Results from Prior NSF Support}

\subsubsection{Award N (\dol{123456}, 2/2019--1/2022) ``REU: Title'' (Lastname, Senior Personnel)}

\paragraph{Intellectual Merit}

Dr. Lastname is part of an expert group of faculty members who mentor REU participants in certain topics, by helping students to
\begin{enumerate*}[label=(\arabic*), itemjoin={{; }}, itemjoin*={{; and }}]
\item conceive, design, implement, and assess research projects in this area
\item learn diverse different toolsets in domains such as example 1, example 2, and example 3.
\end{enumerate*}

\paragraph{Broader Impacts}
Dr. Lastname's portion of the REU provided a research experience to 5 undergraduate students, including 2 female students.

\paragraph{Publications}
To date, this effort has resulted in 4 published papers \cite{paudel2019a,paudel2019b,paudel2018,mookiah2017}, with undergraduate and graduate students as first two authors.

\renewcommand{\bibname}{References Cited}
\printbibliography[heading=bibnumbered]

\end{document}
